Dynamic Modeling for Optimal Cryptoeconomic Policies

### 2023-11-03 Presentations/lightning_slides.tex
update slides

\begin{frame}{Research Question}

@@

    \item Policy goal: maximize welfare for \underline{good actors}: users (increase in token price) and validators (transaction fees)
\end{itemize}

@@

\begin{frame}{Literature Review}
    \begin{itemize}
        \item Micro foundations:\\
        {\footnotesize \textit{\citet{nisan2007algorithmic, budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}, etc.}}\\
        $\rightarrow$ \textbf{Block reward and transaction fee as incentive mechanisms}

@@

\begin{frame}{Contribution to the Literature}
\begin{itemize}
    \item Practical: Most cryptoeconomic systems feature fixed-schedule token supply
    \begin{itemize}
        \item deterministic token supply (Bitcoin\footnote{Satoshi Nakamoto (2008). Bitcoin: A peer-to-peer electronic cash system}), 
        fixed burn rate (Ethereum\footnote{Ethereum Documentation. ``Gas and Fees - Base fees"}), 
        naive dynamic burning (Binance Coin)
    \end{itemize}

    \item No published literature has been established on optimal staking and burning policies for proof-of-stake cryptocurrencies.
\end{itemize}
Novelty of this research:
\begin{itemize}
    \item Applies dynamic general equilibrium methods to model and optimize crypto policies for staking and burning            
      \item Traditional models for optimal fiscal policy (e.g. Ramsey) and monetary policy (e.g. NK) are not directly transferrable to cryptoeconomies due to transaction fee role in the cryptoeconomy

\end{itemize}
\end{frame}

@@

\begin{frame}{Token supply}
    \begin{align}
        M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
        &= M_t + \delta_t L_t - \varphi_t^b X_t
    \end{align}
    $M_t$: total token supply\\
    $X_t \equiv M_t - L_t$: circulating supply \\
    \quad $\Rightarrow$ Token market clearing condition is $X_t=q_t$\\
    \ \\
    $^*$ In reality the total reward is $\delta_t L_t^\alpha$, with pre-set $\alpha\in [0,1]$\footnote{$\alpha=0.5$ for Ethereum. See Ethereum Documentation. ``Proof-of-Stake Rewards and Penalties"}. Here I set $\alpha=1$ WLOG since $\delta_t$ is dynamic.
    % calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
\end{frame}

\begin{frame}{First order conditions}
    * for a deterministic version of the model
    \bigskip

@@

    WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
\end{frame}

%----------------
\section{Calibration}
\begin{frame}{Calibration (idea phase)}
    \begin{itemize}
        \item \textbf{Data sources:} Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
        \item \textbf{Period:} Sep 2022 - now, down to block frequency (12s) 24/7
        \item Proxy for transactional benefits/convenience yields: average onchain txn processing per second $a_t$\citep{cong2022staking}
        \begin{itemize}
            \item other potential proxies: Metcalfe's measure $\log(DailyActiveAddresses^2)$; \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
        \end{itemize}

        \item Proxy for hacking: manually index major hacks and wallet losses
    \end{itemize}
\end{frame}

@@

>>>>

\begin{frame}{Research question}

@@

    \item Policy goal: maximize welfare for \underline{good actors}: users (increase in token price \& consumption) and validators (transaction fees)
\end{itemize}

@@

\begin{frame}{Literature review}
    \begin{itemize}
        \item Micro foundations:\\
        {\footnotesize \textit{\citet{nisan2007algorithmic, budish2018economic, biais2019blockchain, gans2019more, gans2022mechanism, huberman2021monopoly}, etc.}}\\
        $\rightarrow$ \textbf{Block reward and transaction fee as incentive mechanisms}

@@

\begin{frame}{Contribution to the literature}
\begin{itemize}
    \item Practical: Most cryptoeconomic systems feature fixed-schedule token supply, creating highly volatile token prices
    \item Problem: Traditional models for optimal fiscal policy (e.g. Ramsey) and monetary policy (e.g. NK) are not directly transferrable to cryptoeconomies due to transaction fee role in the cryptoeconomy
    % \begin{itemize}
    %     \item deterministic token supply (Bitcoin\footnote{Satoshi Nakamoto (2008). Bitcoin: A peer-to-peer electronic cash system}), 
    %     fixed burn rate (Ethereum\footnote{Ethereum Documentation. ``Gas and Fees - Base fees"}), 
    %     naive dynamic burning (Binance Coin)
    % \end{itemize}
    \item Novel hypothesis: Dynamic token supply (via staking and burning policies) can be used to optimize welfare 
    \begin{itemize}
        \item implement in a dynamic equilibrium model framework
    \end{itemize}
\end{itemize}

@@

\begin{frame}{Token supply}
    \begin{align}
        M_{t+1} &= (M_t - L_t) + L_t (1 + \delta_t) - \varphi_t^b X_t \nonumber \\
        &= M_t + \delta_t L_t - \varphi_t^b X_t
    \end{align}
    $M_t$: total token supply\\
    $X_t \equiv M_t - L_t$: circulating supply \\
    \quad $\Rightarrow$ Token market clearing condition is $X_t=q_t$\\
    \ \\
    $^*$ In reality the total reward is $\delta_t L_t^\alpha$, with pre-set $\alpha\in [0,1]$\footnote{$\alpha=0.5$ for Ethereum. See Ethereum Documentation. ``Proof-of-Stake Rewards and Penalties"}. Here I set $\alpha=1$ for simplicity.
    % calculations: https://blog.bitmex.com/ethereums-proof-of-stake-system-calculating-penalties-rewards/
\end{frame}

\begin{frame}{First order conditions}    
    $^*$ using a deterministic version of the model
    \bigskip

@@

    %WIP: Equilibrium solutions with stochasticity \& log/CRRA preferences
\end{frame}

\begin{frame}{Token market equilibrium}
    \hyperlink{det_math}{\beamerbutton{Appendix: deterministic math}}
    \begin{figure}
        \centering
        \includegraphics[width=\textwidth]{../Figures/det_SD.png}
        \caption{Illustration of token market equilibrium using artificial parameters. Both supply and demand are convex in $q$}
    \end{figure}

%----------------
\section{Calibration}

\begin{frame}{The Ethereum (ETH) blockchain}
    Ethereum (created by V. Buterin in 2013) is currently the second largest cryptoeconomy after Bitcoin.\\
    \bigskip
    Important historical upgrades to Ethereum's tokenomics:
    \begin{itemize}
        \item London upgrade (Aug 2021): introduced base fee burning via EIP-1559
        \item ``The Merge" (Sep 2022): transition from computing-based (PoW) to staking-based issuance (PoS) i.e. Ethereum 2.0
        \item Shanghai-Capella upgrade (Apr 2023): unlocked withdrawls of staked ETH \footnote{Hypothesis: this changes validators' staking behaviors}
    \end{itemize}
\end{frame}

\begin{frame}{Ethereum 2.0 data}
    Despite having only 6-12 months of history, Ethereum 2.0 data is rich and highly accessible:
    \begin{itemize}
        \item All transactions are publicly broadcasted to the blockchain every 12 seconds (block time), 24/7
        \item All validators' staking actions and rewards are also recorded
        \item ETH-USD price data are available from both onchain sources (DEX) and offchain (CEX/``oracle") sources
    \end{itemize}

\begin{frame}{Features for calibration}
    \begin{itemize}
        \item Method: baseline - OLS; advanced - VAR
        \item Data sources: Ethereum prices from Messari API, txn fees from Dune Analytics, staking data from beaconcha.in
        \item Proxy for transactional benefits/convenience yields: 
        \begin{itemize}
            \item Throughput measures: average onchain txn processing per second \citep{cong2022staking}; user operations per second (new measure proposed by industry researchers)
            \item Network-based measures: Metcalfe's measure $\log(DailyActiveAddresses^2)$; 
            \item Additional controls: \href{https://www.ncsl.org/financial-services/cryptocurrency-2023-legislation}{index on US crypto regulation (NCSL.org)}
        \end{itemize}
        \item Proxy for hacking: manually index major hacks and wallet losses (problem: frequency is much lower than txn/staking actions)
    \end{itemize}
\end{frame}

@@

\section{Appendix}
\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
    \label{det_math}
    \begin{align}
        \intertext{Inverse demand curve:}
        q_t &= \left[ \beta \frac{e_t^u}{p_t} - (1+\beta)m_t \frac{\hat{p}_t}{p_t} \right] \cdot\\
            & \left[\beta(1+ \varphi_t^b+\varphi_t^v) + \frac{(1-h_{t+1})(1+\theta_{t+1})}{1+r_t} \frac{p_{t+1}}{p_t}\right]^{-1}\\
        \intertext{Inverse supply curve:}
        q_t &= \left(1+\frac{\beta}{1+\beta}\varphi_t^v\right)^{-1} \left(M_t - \frac{\beta}{1+\beta}\frac{e_t^v}{p_t}\right)
    \end{align}

\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
    \begin{align}
        \intertext{Token market clearing implies $\frac{1}{p_t^*}$ must satisfy the quadratic equation}
        A_t \frac{1}{p_t^*} &= (M_t + B_t\frac{1}{p_t^*}) (C_t + D_t\frac{1}{p_t^*}) \\
        \intertext{where}
        A_t &:= \left[ \beta e_t^u - (1+\beta)m_t \hat{p}_t \right] \left(1+\frac{\beta}{1+\beta}\varphi_t^v\right);\quad
        B_t := - \frac{\beta}{1+\beta} e_t^v;\\
        C_t &:= \beta(1+ \varphi_t^b+\varphi_t^v);\quad
        D_t := \frac{(1-h_{t+1})(1+\theta_{t+1})}{1+r_t} p_{t+1}
        \end{align}
\end{frame}

\begin{frame}[noframenumbering]{Deterministic solutions (cont.)}
    \begin{align}
        \intertext{Therefore the closed-form solution for equilibrium token price is given by}
        p_t^* &= \frac{2B_tD_t}{A_t-M_t D_t-B_tC_t - \sqrt{(M_t D_t+B_t C_t-A_t)^2-4M_t B_tC_tD_t}}\\
        \intertext{under some technical conditions.}\nonumber
    \end{align}
